Modal Abstractions for Virtualizing Memory Addresses

### 2025-07-30 examples_C.tex
delete stray A that was probably from a vim/hx edit more mixup

\begin{figure}\footnotesize
  \begin{lstlisting}[language=C,mathescape,escapeinside={(*}{*)}]
/* @param entry: virtual address of a non-present entry to initialize with a new physical page */
$\specline{\textsf{P} \ast  I\texttt{ASpace}_{\textsf{id}}(\theta,\Xi,m) \ast \lnot(\textsf{entry\_present entryv}) \ast \textsf{entryp+KERNBASE} \mapsto_{\textsf{vpte,1}} \textsf{entryp entryv} \ast \ghostmaptoken{\textsf{id}}{(\mathsf{entryp})}{\textsf{level}} }$
void pte_initialize(pte_t *entry) {
  pte_t *local = kalloc(); // Allocate a full zeroed page for 512 8-byte entries(*\label{line:call_to_kallocC}*)
  entry->pfn = PTE_ADDR_TO_PFN((uintptr_t) local);(*\label{line:kalloc_install}*)
  $\specline{\textsf{P} \ast  I\texttt{ASpace}_{\textsf{id}}(\theta,\Xi,m) \ast \lnot(\textsf{entry\_present entryv}) \ast \textsf{entryp+KERNBASE} \mapsto_{\mathsf{vpte,1}} \mathsf{entryp} \; \textsf{pfn\_set(entryv nextpaddr)}}$
  $\specline{\ghostmaptoken{\delta{}s}{\rtv}{\delta} \ast \forall_{i\in\textsf{0..511}}\ldotp ()\textsf{table\_root (pte\_initialized (pfn\_set (entry\_val nextpaddr))) + i * 8}) \mapsto_{\textsf{id}} \textsf{level-1}   }_{\rtv}$(*\label{line:initialize_post}*)A
}
\end{lstlisting}
\vspace{-2em}
\caption{Allocating a physical page }
\label{pteinitializespecC}
\vspace{-1em}
\end{figure}

>>>>

\begin{figure}\footnotesize
  \begin{lstlisting}[language=C,mathescape,escapeinside={(*}{*)}]
/* @param entry: virtual address of a non-present entry to initialize with a new physical page */
$\specline{\textsf{P} \ast  I\texttt{ASpace}_{\textsf{id}}(\theta,\Xi,m) \ast \lnot(\textsf{entry\_present entryv}) \ast \textsf{entryp+KERNBASE} \mapsto_{\textsf{vpte,1}} \textsf{entryp entryv} \ast \ghostmaptoken{\textsf{id}}{(\mathsf{entryp})}{\textsf{level}} }$
void pte_initialize(pte_t *entry) {
  pte_t *local = kalloc(); // Allocate a full zeroed page for 512 8-byte entries(*\label{line:call_to_kallocC}*)
  entry->pfn = PTE_ADDR_TO_PFN((uintptr_t) local);(*\label{line:kalloc_install}*)
  $\specline{\textsf{P} \ast  I\texttt{ASpace}_{\textsf{id}}(\theta,\Xi,m) \ast \lnot(\textsf{entry\_present entryv}) \ast \textsf{entryp+KERNBASE} \mapsto_{\mathsf{vpte,1}} \mathsf{entryp} \; \textsf{pfn\_set(entryv nextpaddr)}}$
  $\specline{\ghostmaptoken{\delta{}s}{\rtv}{\delta} \ast \forall_{i\in\textsf{0..511}}\ldotp ()\textsf{table\_root (pte\_initialized (pfn\_set (entry\_val nextpaddr))) + i * 8}) \mapsto_{\textsf{id}} \textsf{level-1}   }_{\rtv}$(*\label{line:initialize_post}*)
}
\end{lstlisting}
\vspace{-2em}
\caption{Allocating a physical page }
\label{pteinitializespecC}
\vspace{-1em}
\end{figure}
